Effects of Fishing on Scarid Grazing Behavior in the Caribbean

### 2018-01-07 DonorReport.Rmd
update for antigua fisheries

My research aims to document variations in grazing behavior across different reef conditions, testing for the effects of parrotfish abundance, predator abundance, and benthic condition on the amount of time parrotfish spend feeding, their bite rates, and the duration of their feeding bouts. Bonaire represents a relatively pristine Caribbean system, while Antigua has shifted to a more algal-dominated, low scarid state. I also conducted surveys in Barbuda, where a recent efforts to reduce parrotfish fishing may have interesting implications on grazing behavior.

@@

In August of 2017, I set out to document parrotfish feeding behaviors in Antigua and Barbuda, two neighboring islands with historical overfishing and relatively degraded reefs systems. While parrotfish fishing continues in Antigua, a parrotfish fishing ban has recently been instated in Barbuda. Both of these islands would serve as comparisons to the pristine system in Bonaire that are more represenative of reef status in the larger Caribbean region.

Thanks to generous funding awarded through the UCSB Research Accellerator Award, I was able to travel to Antigua along with a research assistant also working on her Ph.D. in marine ecoogy and fisheries management. The funds supplied us with SCUBA tanks, survey gear, boat fuel, a car rental to transport gear, and fuel and food to supply a four-day boat trip to Barbuda. During the three weeks we were in the field, we collected benthic and fish survey data at a total of nine sites which, in addition to providing data for this investigation, will also serve as valuable assessment and baseline data for future studies. Across the nine sites we coolected behavioral data from a total of 434 individual parrotfish, making a database of nearly 800 fish follows when integrated with the data I collected in Bonaire. While the data analysis is still ongoing, the preliminary results are extremely interesting. This research would not have been possible without the generous support of my Research Accellerator sponsor.

>>>>

My research aims to document variations in grazing behavior across different reef conditions, testing for the effects of parrotfish abundance, predator abundance, and benthic condition on the amount of time parrotfish spend feeding, their bite rates, and the duration of their feeding bouts.

@@

In January and August of 2017, I set out to document parrotfish feeding behaviors in Antigua and Barbuda, two neighboring islands with historical overfishing and relatively degraded reefs systems. While parrotfish fishing continues in Antigua, a parrotfish fishing ban has recently been instated in Barbuda. Both of these islands would serve as comparisons to the pristine system in Bonaire that are more represenative of reef status in the larger Caribbean region. Thanks to help from Ms. Appleton and Ms. Lovell at Antigua Fisheries, Dr. Cooper at Antigua National Parks, and Mr. Morris from Barbuda, I received permission to conduct my surveys as well as useful information about fishing pressure around the islands. I would also like to thank Ruleo Camacho for his continued help and feedback.

With the support of generous funding awarded through the UCSB Research Accellerator Award, I was able to travel to Antigua along with a Julia Mason, a research assistant also working on her Ph.D. in marine ecoogy and fisheries management at Stanford University. The funds supplied us with SCUBA tanks, survey gear, boat fuel, a car rental to transport gear, and fuel and food to supply a four-day boat trip to Barbuda. During the three weeks we were in the field, we collected benthic and fish survey data at a total of nine sites which, in addition to providing data for this investigation, will also serve as valuable assessment and baseline data for future studies. Across the nine sites we coolected behavioral data from a total of 434 individual parrotfish, making a database of nearly 800 fish follows when integrated with the data I collected in Bonaire. While the data analysis is still ongoing, the preliminary results are extremely interesting. This research would not have been possible without the generous support of my Research Accellerator sponsor.

```{r, eval=FALSE}
Thanks to generous funding awarded through the UCSB Research Accellerator Award, I was able to travel to Antigua along with a research assistant also working on her Ph.D. in marine ecoogy and fisheries management. The funds supplied us with SCUBA tanks, survey gear, boat fuel, a car rental to transport gear, and fuel and food to supply a four-day boat trip to Barbuda. During the three weeks we were in the field, we collected benthic and fish survey data at a total of nine sites which, in addition to providing data for this investigation, will also serve as valuable assessment and baseline data for future studies. Across the nine sites we coolected behavioral data from a total of 434 individual parrotfish, making a database of nearly 800 fish follows when integrated with the data I collected in Bonaire. While the data analysis is still ongoing, the preliminary results are extremely interesting. This research would not have been possible without the generous support of my Research Accellerator sponsor.
```
